ZCB Pricing

### 2018-07-29 ZCB Pricing .Rmd
sensitivity test part 1

>>>>

senses <- matrix(nrow=10, ncol=9) # matrix to hold prices for various parameters
colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")

#Initial Parameters
senses[1,2]=bond_price()
senses[1,3]=Crude_Monte_Carlo()
senses[1,4]=Antithetic_variates()
senses[1,5]=Moment_Matching()
senses[1,6]=Control_Variates_estimate()
senses[1,7]=explicit()
senses[1,8]=implicit()
senses[1,9]=CN()

#r=0.1
senses[2,2]=bond_price(r=0.1)
senses[2,3]=Crude_Monte_Carlo(r=0.1)
senses[2,4]=Antithetic_variates(r=0.1)
senses[2,5]=Moment_Matching(r=0.1)
senses[2,6]=Control_Variates_estimate(r=0.1)
senses[2,7]=explicit(r=0.1)
senses[2,8]=implicit(r=0.1)
senses[2,9]=CN(r=0.1)
```
